---
title: "Pre-registered analysis"
author: "Ben Smith"
date: "4/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, include=FALSE}
library(ggplot2)
library(lme4)
source("load_and_preprocess_compiled_data20180330.R")

print(data.itc[,.N,by=.(SubjectUniqueID,ConditionCode)] %>% .[,.N,by=ConditionCode])

```


```{r setup3, include=FALSE}
#we were going to throw out subjects with lots of L or R, subjects with very low k-values, subjects with low response rates, or where they choose less than 16.7% of LEFT or RIGHT or 1 or 2 responses.

too_selective_subjs<-data.itc[,.(LeftProp=sum(ChoiceKey==1,na.rm = TRUE)/sum(!is.na(ChoiceKey)),RightProp=sum(ChoiceKey==2,na.rm = TRUE)/sum(!is.na(ChoiceKey)),finalK=endingK[.N]),by=.(SubjectUniqueID)] %>% 
  .[LeftProp<.167 | LeftProp>(1-.167) | finalK<=0.0001,SubjectUniqueID]
data.itc<-data.itc[!(SubjectUniqueID %in% too_selective_subjs)]

data.itc[,.(NAChoices=sum(is.na(ChoiceKey))),by=.(SubjectUniqueID)] %>% .[order(NAChoices)]
table(data.itc[SubjectUniqueID=="M730ARVGMonApr092018184028GMT0200CEST37168831",.(Choice,ChoiceKey,SSonLorR)])
```
## Intro

This analysis closely folloiws the analysis that I prespecified before collecting data on https://osf.io/8te4b/ . At that location, it is embargoed, but it is also available at https://osf.io/uhgwn/ for our team internally.

##Deviation from pre-registration

The SmallerSooner amount in the FixedAmount condition changed from \$0.50 to \$0.40, after the first round, in which it seemed like subjects in that condition were too strongly biased toward SmallerSooner.

Due to a technical error, one group of subjects were incorrectly told rewards were real when they were actually hypothetical. These have been excluded from the current analysis.

We introduced an extra between-subjects variable, Hypothetical vs. Real, that was not described on the uploaded pre-registration (I'd intended to upload this, but uploaded the older version of the pre-registration by mistake). To maintain a 3x2x2 between-subjects design, SalienceCondition was moved to be a within-subjects, between-trials variable.

## Aims/hypotheses

For this study, we want to test this predictions relevant to construal level:

1. A Construal Level manipulation has an effect on temporal discounting, such that more abstract construal level manipulations predict lower rates of temporal discounting
  a. This relationship will be observable with random construal order
  b. This relationship will be observable with the abstract to concrete and the concrete to abstract construal order conditions, OR
  c. This relationship will only be observable in the direction observed by Yi et al. (2017), i.e., only among participants who view the concrete condition prior to the abstract prediction
  d. This relationship will be observable in the interleaved conditions
  e. This relationship will be observable in the blocked conditions

We also want to test these predictions relevant to sugar manipulation:

2. Across other manipulations, participants will exhibit steeper delay discounting in test blocks in which Amount is fixed compared to blocks in which Delay is fixed (“block type”).
3. There will be an interaction between block type and fatigue/appetite, such that high appetite/fatigue scores will be associated with the larger block type differential in discounting

### Supplementary predictions:
1. (as above)
  f. This relationship will be observable when displaying hypothetical rewards
  g. This relationship will be observable when displaying real rewards

## Measures

We can characterize subject’s choice in each trial in two ways:

1. the absolute choice of LargerLater vs. SmallerSooner
2. the deviation of each choice from the expected present value, estimated the expected present value using the estimate for the subject’s k value obtained at the end of each run of the task.

## Results

### 1. A Construal Level manipulation has an effect on temporal discounting, such that more abstract construal level manipulations predict lower rates of temporal discounting

```{r}
#absolute choice of largerlater vs. smallersooner
#needs to be further pre-processed so every row reflects a trial with a construal level and a choice
table(data.to.analyze$ConstrualConditionAllocated,data.to.analyze$Choice)
table(data.to.analyze$Choice,data.to.analyze$Choice01)
table(is.na(data.to.analyze$ConstrualConditionAllocated))
table(is.na(data.to.analyze$Choice))
table(is.na(data.to.analyze$Choice))

choicemodel.base.VarySubSlope<-lmer(AbstractionLevel~(1+ChoiceIsLL|SubjectUniqueID),data.itc, control = lmerControl(optimizer = "Nelder_Mead"))
choicemodel.choice.VarySubSlope<-lmer(AbstractionLevel~ChoiceIsLL+(1+ChoiceIsLL|SubjectUniqueID),data.itc, control = lmerControl(optimizer = "Nelder_Mead"))
summary(choicemodel.base.VarySubSlope)
summary(choicemodel.choice.VarySubSlope)
anova(choicemodel.base.VarySubSlope,choicemodel.choice.VarySubSlope)


```
#### This relationship will be observable with random construal order
```{r}

choicemodel.base.VarySubSlope.rand<-lmer(AbstractionLevel~(1+ChoiceIsLL|SubjectUniqueID),data.itc[BlockDesignRandomized==TRUE], control = lmerControl(optimizer = "Nelder_Mead"))
choicemodel.choice.VarySubSlope.rand<-lmer(AbstractionLevel~ChoiceIsLL+(1+ChoiceIsLL|SubjectUniqueID),data.itc[BlockDesignRandomized==TRUE], control = lmerControl(optimizer = "Nelder_Mead"))
summary(choicemodel.base.VarySubSlope.rand)
summary(choicemodel.choice.VarySubSlope.rand)
anova(choicemodel.base.VarySubSlope.rand,choicemodel.choice.VarySubSlope.rand)

```
Not when using random construal order at all.

#### This relationship will be observable with the construal-ordered conditions
```{r}

choicemodel.base.VarySubSlope.AF<-lmer(AbstractionLevel~(1+ChoiceIsLL|SubjectUniqueID),data.itc[BlockDesignAbstractFirst==TRUE], control = lmerControl(optCtrl=list(method="L-BFGS-B")))

library(optimx)
choicemodel.base.VarySubSlope.CF<-lmer(AbstractionLevel~(1+ChoiceIsLL|SubjectUniqueID),data.itc[BlockDesignConcreteFirst==TRUE], control = lmerControl(optimizer="optimx",optCtrl=list(method="L-BFGS-B")))
choicemodel.choice.VarySubSlope.AF<-lmer(AbstractionLevel~ChoiceIsLL+
                                           (1+ChoiceIsLL|SubjectUniqueID),data.itc[BlockDesignAbstractFirst==TRUE], control = lmerControl(optimizer = "bobyqa"))

choicemodel.choice.VarySubSlope.CF<-lmer(AbstractionLevel~ChoiceIsLL+
                                           (1+ChoiceIsLL|SubjectUniqueID),data.itc[BlockDesignConcreteFirst==TRUE], control = lmerControl(optimizer = "bobyqa"))

summary(choicemodel.choice.VarySubSlope.AF)
anova(choicemodel.base.VarySubSlope.AF,choicemodel.choice.VarySubSlope.AF)

summary(choicemodel.choice.VarySubSlope.CF)
anova(choicemodel.base.VarySubSlope.CF,choicemodel.choice.VarySubSlope.CF)

```

#### This relationship will only be observable among participatns who view the concrete condition prior to the abstract prediction

As above - this doesn't quite check out.


#### This relationship will only be observable among participants in interleaved conditions
(because the interleaved design will have a more immediate impact on the construal condition)
```{r}
choicemodel.base.VarySubSlope.inter<-lmer(AbstractionLevel~(1+ChoiceIsLL|SubjectUniqueID),data.itc[TaskArrangementBlocked==FALSE], control = lmerControl(optimizer = "Nelder_Mead"))
choicemodel.choice.VarySubSlope.inter<-lmer(AbstractionLevel~ChoiceIsLL+(1+ChoiceIsLL|SubjectUniqueID),data.itc[TaskArrangementBlocked==FALSE], control = lmerControl(optimizer = "Nelder_Mead"))
summary(choicemodel.base.VarySubSlope.inter)
summary(choicemodel.choice.VarySubSlope.inter)
anova(choicemodel.base.VarySubSlope.inter,choicemodel.choice.VarySubSlope.inter)

```

#### This relationship will only be observable among participants in blocked conditions
(because the effect is more concentrated)
```{r}

choicemodel.base.VarySubSlope.inter<-lmer(AbstractionLevel~(1+ChoiceIsLL|SubjectUniqueID),data.itc[TaskArrangementBlocked==TRUE], control = lmerControl(optimizer = "Nelder_Mead"))
choicemodel.choice.VarySubSlope.inter<-lmer(AbstractionLevel~ChoiceIsLL+(1+ChoiceIsLL|SubjectUniqueID),data.itc[TaskArrangementBlocked==TRUE], control = lmerControl(optimizer = "Nelder_Mead"))
summary(choicemodel.base.VarySubSlope.inter)
summary(choicemodel.choice.VarySubSlope.inter)
anova(choicemodel.base.VarySubSlope.inter,choicemodel.choice.VarySubSlope.inter)

```


## Possible thing to try out in the scanner.

This is what I would like to try in the scanner. Does Interleaved work where we've got a concrete to abstract design?


```{r}

t.test(AbstractionLevel~Choice,data.to.analyze[TaskArrangement=="TasksInterleaved" & Group=="BlockDesign_concrete_first"]) 
t.test(AbstractionLevel~Choice,data.to.analyze[TaskArrangement=="TasksBlocked" & Group=="BlockDesign_concrete_first"]) 
t.test(AbstractionLevel~Choice,data.to.analyze[TaskArrangement=="TasksBlocked" & Group=="BlockDesign_abstract_first"]) 

```

